Standardization of ceramic shape: A case studay from the Iron Age pottery from northeastern Taiwan

### 2020-07-29 analysis/paper/paper.Rmd
resolve merge conflict
polish some of the plots a little bit

# what are the variences for each PC in each period?
len <- length(op.p$x[,1])

@@

@@

# making the cv label
cv_label <-
  cv_pcs_all %>% 
  mutate(cv_pc1 = paste("CV=", cv_pc1, "%"),
         cv_pc2 = paste("CV=", cv_pc2, "%"),
         cv_pc3 = paste("CV=", cv_pc3, "%"))

@@

ggplot(pc_plot,
       aes(phase,
           pc)) +
  geom_violin() + 
  ggforce::geom_sina() +
  xlab("") +
  facet_wrap(~ pcn, ncol = 1) +
  geom_text(data = cv_pcs_all,
            mapping = aes(x = c(2.1, 1.1, 3.1, 2.1, 1.1, 3.1, 2.1, 1.1, 3.1), 
                          y = 8.5, 
                          label = cv_label),
            size = 3,
            color= "red",
            hjust = -0.1,
            vjust= -1)+
  theme_minimal()

@@

```{r boxplot-size-by-phase}
# size boxplot by period
boxplot_size <-
  ggplot(jpgs_imported_coo_size_pcs_metric,
         aes(Diameter1_Body, fct_rev(y))) +
  geom_boxplot() +
  coord_flip() +
  labs(x = "body diameter (mm)", y = "") +
  scale_y_discrete(breaks = c("Pre-European", "Post-European", "Chinese"),
                   labels = c("Pre-\nEuropean", "Post-\nEuropean", "Chinese")) +
  theme(axis.text = element_text(size = 8))
```

```{r pcs-size-regression}
# can pc1 predict size by period?
pc1_size_reg <- 
  ggscatter(jpgs_imported_coo_size_pcs_metric, 
            x = "Diameter1_Body", 
            y = "pc1",
            add = "reg.line",
            size = 1) +
    facet_wrap(~ fct_rev(y)) +
    stat_cor(label.y = 10, label.sep = "\n") +
    #stat_regline_equation(label.y = 1) +
    labs(x = "", y = "PC1") +
    theme(axis.text = element_text(size = 8)) +
    #scale_x_continuous(breaks = c(75, 200)) +
    scale_y_continuous(limits = c(0, 12),
                       breaks = c(seq(0, 10, 2)),
                       labels = c(seq(0, 10, 2)))

# can pc2 predict size by period?
pc2_size_reg <- 
  ggscatter(jpgs_imported_coo_size_pcs_metric, 
            x = "Diameter1_Body", 
            y = "pc2",
            add = "reg.line",
            size = 1) +
    facet_wrap(~ fct_rev(y)) +
    stat_cor(label.y = 10, label.sep = "\n") +
    #stat_regline_equation(label.y = 1) +
    labs(x = "body diameter (mm)", y = "PC2") +
    theme(axis.text = element_text(size = 8)) +
    #scale_x_continuous(breaks = c(75, 200)) +
    scale_y_continuous(limits = c(0, 12),
                       breaks = c(seq(0, 10, 2)),
                       labels = c(seq(0, 10, 2)))
```

>>>>

# what are the variances for each PC in each period?
len <- length(op.p$x[,1])

@@

pc_cv_table <- 
pc_plot %>% 
  group_by(phase, pcn) %>% 
  summarise(cvs = raster::cv(pc)) %>% 
  pivot_wider(names_from = pcn, 
              values_from = cvs)

@@

# making the cv label
cv_label <-
  cv_pcs_all %>% 
  mutate(cv_pc1 = paste("CV = ", cv_pc1, "%"),
         cv_pc2 = paste("CV = ", cv_pc2, "%"),
         cv_pc3 = paste("CV = ", cv_pc3, "%"))

@@

ggplot(pc_plot,
       aes(phase,
           pc)) +
  geom_violin() + 
  ggforce::geom_sina() +
  xlab("") +
  facet_wrap(~ pcn, ncol = 1) +
  geom_text(data = cv_pcs_all,
            mapping = aes(x = c(2.1, 1.1, 3.1, 2.1, 1.1, 3.1, 2.1, 1.1, 3.1), 
                          y = 8.5, 
                          label = cv_label),
            size = 2,
            color= "red",
            hjust = -0.1,
            vjust= -1)+
  theme_minimal()

@@

```{r boxplot-size-by-phase}
# size boxplot by period
boxplot_size <-
  ggplot(jpgs_imported_coo_size_pcs_metric,
         aes(Diameter1_Body, fct_rev(y))) +
  geom_boxplot() +
  coord_flip() +
  labs(x = "body diameter (mm)", y = "") +
  scale_y_discrete(breaks = c("Pre-European", "Post-European", "Chinese"),
                   labels = c("Pre-\nEuropean", "Post-\nEuropean", "Chinese")) +
  theme(axis.text = element_text(size = 8)) +
  theme_bw()
```

```{r pcs-size-regression}
# can pc1 predict size by period?
pc1_size_reg <- 
  ggscatter(jpgs_imported_coo_size_pcs_metric, 
            x = "Diameter1_Body", 
            y = "pc1",
            add = "reg.line",
            size = 1) +
    facet_wrap(~ fct_rev(y)) +
    stat_cor(label.y = 11, 
             label.sep = ", ",
             size = 2) +
    #stat_regline_equation(label.y = 1) +
    labs(x = "", y = "PC1") +
    theme(axis.text = element_text(size = 8)) +
    #scale_x_continuous(breaks = c(75, 200)) +
    scale_y_continuous(limits = c(0, 12),
                       breaks = c(seq(0, 10, 2)),
                       labels = c(seq(0, 10, 2)))

# can pc2 predict size by period?
pc2_size_reg <- 
  ggscatter(jpgs_imported_coo_size_pcs_metric, 
            x = "Diameter1_Body", 
            y = "pc2",
            add = "reg.line",
            size = 1) +
    facet_wrap(~ fct_rev(y)) +
    stat_cor(label.y = 11, 
             label.sep = ", ",
             size = 2) +
    #stat_regline_equation(label.y = 1) +
    labs(x = "body diameter (mm)", y = "PC2") +
    theme(axis.text = element_text(size = 8)) +
    #scale_x_continuous(breaks = c(75, 200)) +
    scale_y_continuous(limits = c(0, 12),
                       breaks = c(seq(0, 10, 2)),
                       labels = c(seq(0, 10, 2)))
```
